# Rmd è il di markdown
# ho creato Readme

---
title: "MarkdownReport"
author: "Duccio Rocchini"
date: "2024-01-09"
output: html_document
---

# My first markdown document!

Here you can add some text if you want!

In this case you attain a result: 
```{r, eval=T}
2 + 3
```

In this case you do not:
```{r, eval=F}
2 + 3
```

Using proper packages; the imageRy package has been nuilt at Alma Mater for learning remote sensing:
```{r, eval=T}
library(imageRy)
```

Let's import tha data by listing them in imageRy:
```{r, eval=T}
im.list()
```

Importing the Mato grosso area image:
```{r, eval=T}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Importing the Mato grosso area image without warnings:
```{r, eval=T, warning=F}
mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Making a new plot of the Mato Grosso area with the NIR ontop of the green component of the RGB space:
```{r, eval=T}
im.plotRGB(mato1992, r=2, g=1, b=3)
```

Plotting several images altogether:
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=1)
```

Calculating spectral indices:
```{r, eval=T}
library(terra)
library(viridis)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
```

Calculating variability:
```{r, eval=T}
sd5 <- focal(mato1992[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=viridisc)
```

MIO LEZIONE
---
title: "Vignette"
author: "Klizia Spinelli"
date: "2024-05-16"
output:
  pdf_document: default
  html_document: default
---


```{r}
library(terra)
library(imageRy)
library(viridis)
```


```{r, eval=T}
mato <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

This plot is related to the following bands: band 1 = NIR, band 2 = red, band 3 = green

We are using a set from Mato Grosso, and we can plot it in a RGB space, as:

```{r, eval=T}
im.plotRGB(mato, 1, 2, 3)
```
Look at different band combinations altogether we can use:


```{r, eval=T}
par(mfrow=c(1,3))
im.plotRGB(mato, 1, 2, 3)
im.plotRGB(mato, 2, 1, 3)
im.plotRGB(mato, 3, 2, 1)
```
## calculating spectral indices
```{r, eval=T}
library(terra)
dvi <- mato [[1]] - mato [[2]]
plot(dvi)
```
non va se non metto il cìpacchetto terra per cui lo metto sopra nei pacchetti usati


## Calculating spatial variability
```{r, eval=T}
sd5 <- focal(mato1992[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=magma(100))
```

matrid da 1 pix fino a 25 di 5x5 pixel con la funz che è standar deviation. l'importnante è non chiamarla anche sd xk si chiama cosi la funzione

accanto a knitr c'è knotr to pdf e dovrebbe venir fuori un pdf via latex
non sempre funziona xk bisonga installare un compilatore interno


Aggiungere al curriculum v Markdown e Latex

ultimo passaggio
6 giungo
19 giungo aula D
10 luglio aula C
7 agosto aula magna atonomia comparata via selmi 3
11 settembre aula D
25 settembre aula D

altro linguaggio Besh

PASSAGGI ESAME
fase uno: commenti
fase due sviluppo progetto script a parte con tt progeto
fase tre presentazione di 10 minuti
codice e risultati
nella presentazione mettere tutti i pezzi di codice
vari siti x scaricare i dati
evento che mi piace
domante: da quale pacchetto deriva, quale altra funzione potrei usare? ecc ecc









